Subject-specific curves for time series forecasting of smart meter demand

### 2019-11-13 sscts-paper-1.Rmd
Add Rob and Souhaib as co-authors

---
title: "Subject-specific curves for time series forecasting of smart meter demand"
author: "Cameron Roach^[Corresponding author. E-mail address: cameron.roach@monash.edu (C. Roach).]"
fontsize: 11pt
papersize: a4
bibliography: ["library.bib", "packages.bib"]
biblio-style: authoryear-comp
subparagraph: true
toc: false
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
output:
  bookdown::pdf_document2:
  # MonashEBSTemplates::workingpaper:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    keep_tex: no
    number_sections: yes
    citation_package: biblatex
---

>>>>

---
title: "Subject-specific curves for time series forecasting of smart meter demand"
author: "Cameron Roach^[Corresponding author. E-mail address: cameron.roach@monash.edu (C. Roach).], Rob Hyndman, Souhaib Ben Taieb"
fontsize: 11pt
papersize: a4
bibliography: ["library.bib", "packages.bib"]
biblio-style: authoryear-comp
subparagraph: true
toc: false
header-includes:
  - \usepackage[left]{lineno}
  - \linenumbers
output:
  bookdown::pdf_document2:
  # MonashEBSTemplates::workingpaper:
    fig_caption: yes
    fig_height: 5
    fig_width: 8
    keep_tex: no
    number_sections: yes
    citation_package: biblatex
---
